\section{Conclusion}

In this work we have presented a discourse-driven approach to narrative 
generation in contrast to most existing work within the computational 
creativity community, which has primarily followed a pipelined approach.
We initially designed our system to pay attention to mostly textual
factors in comic discourse: the repetition of comic actants across the
narrative provides a minimal cohesive backbone on which to pin comic 
understanding.
%
However, as discussed, this form of generation could generate non-sensical
output (e.g. ending comics with a \emph{meanwhile} discourse transition). 
We therefore appealed to more cognitively-oriented factors via the theory
of visual grammar, which helped structure the output in a way that enables
other senses of relatedness to contribute to the output's coherence.
%
Thus, through our small-scale system, we have begun to explore the scale and
limits of human story sense-making faculties, as well as how they come to
bear on narrative generation systems: in our case, through both local and 
global procedures, which inform cohesion and coherence, respectively. 
%
Our algorithms and implementation offer a promising starting point for the
computational investigation of discourse-driven narrative.

More broadly, our work highlights the importance of looking to human
cognition as a point of departure for the design of narrative generators.
Other scholars~(e.g.
\citeauthor{gervas2009computational}~\citeyear{gervas2009computational}, 
\citeauthor{szilas2010requirements}~\citeyear{szilas2010requirements})
have argued the same point; our system provides a computational system
that demonstrates it. Concretely, the reason for this is that humans 
bring significant cognitive faculties to bear on the process of narrative 
comprehension~\cite{herman2013storytelling}. 
An instance of this narrative intelligence is our unique ability to fill 
in the blanks in the liminal spaces of discourse, which (at least) relies on  
our focalized perspectives into the story world~\cite{genette1983narrative}.
As our generated comics show, our narrative sense-making abilities allow us 
to intuit and impose narrative structure on the sequence of depicted images, 
due to how we fill in the blanks left unspecified in our comics. Therefore,
this mental process has a significant role in our appreciation of the 
narrative artifact, and should have an equally significant role in the
generation of it.
